Paper analysis

### 2025-03-28 Paper_analysis.Rmd
update site again

```{r shap_pol_margshap}
grid.arrange(
  sv_dependence(ex.polmarg.glb, v="ntr_pland")
)

@@

```{r shap_sed_baseshap}
grid.arrange(
  sv_dependence(ex.sedbase.glb, v="ann_agr_ed")
)

@@

```{r shap_sed_margshap}
grid.arrange(
  sv_dependence(ex.sedmarg.glb, v="ann_agr_ed"),
  sv_dependence(ex.sedmarg.glb, v="field_frac_mn"),
  ncol=2
)

@@

```{r shap_qb_baseshap}
grid.arrange(
  sv_dependence(ex.qbbase.glb, v="field_frac_mn")
)

@@

```{r shap_qb_margshap}
grid.arrange(
  sv_dependence(ex.qbmarg.glb, v="prn_ann_ratio"),
  sv_dependence(ex.qbmarg.glb, v="prn_agr_para_mn"),
  ncol=2
)

>>>>

```{r shap_pol_margshap, fig.width=9}
grid.arrange(
  sv_dependence(ex.polmarg.glb, v="ntr_pland")
)

@@

```{r shap_sed_baseshap, fig.width=9}
grid.arrange(
  sv_dependence(ex.sedbase.glb, v="ann_agr_ed")
)

@@

```{r shap_sed_margshap, fig.width=9}
grid.arrange(
  sv_dependence(ex.sedmarg.glb, v="ann_agr_ed"),
  sv_dependence(ex.sedmarg.glb, v="field_frac_mn"),
  ncol=2
)

@@

```{r shap_qb_baseshap, fig.width=9}
grid.arrange(
  sv_dependence(ex.qbbase.glb, v="field_frac_mn")
)

@@

```{r shap_qb_margshap, fig.width=9}
grid.arrange(
  sv_dependence(ex.qbmarg.glb, v="prn_ann_ratio"),
  sv_dependence(ex.qbmarg.glb, v="prn_agr_para_mn"),
  ncol=2
)
